Upper Limits on CN from Falling Evaporating Bodies\\seen towards Beta Pictoris

### 2023-01-04 src/tex/ms.tex
[showyourwork] overleaf sync

Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI).

@@

\subsection{HARPS observations}
We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and May 2018. Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years. Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds.

>>>>

Short Beta pic description, previous detection of species in optical (CaII, NaI, FeI). HELLO WORLD!

@@

\subsection{HARPS observations}
We collated all publicly available HARPS observations of $\beta$ Pic obtained between October 2003 and March 2020. Although these observations cover a large baseline, the cadence between visits varies between 1 day and $\sim$2.2 years. Similarly, the number of observations per epoch spans a wide range, between 1 and 356 exposures, while the exposure times vary between 12 and 900 seconds. For this analysis we used the E2DS files downloaded directly from the ESO archive.
